### 2015-04-06 motivation.tex

\noindent To prevent \cf{getBalance} from ever showing negative balance, it is
necessary to prevent the scenario depicted in
fig.~\ref{fig:negativeBalanceAnomaly}. Let $\cureff$ stand for the effect
emitted by the \cf{getBalance} operation. If the effect ($b$) of a withdraw
operation is visible to $\cureff$, and the effect ($a$) of a deposit operation
is visible to the effect ($b$) of the withdraw operation, then it must be the
case that $a$ is also visible to $\cureff$. A contract ($\cv_{gb}^1$) for
\cf{getBalance} operation precisely captures this application-level consistency
requirement:

@@

\noindent To prevent the missing update anomaly described in
fig.~\ref{fig:missingUpdateAnomaly}, it is necessary for a \cf{getBalance}
operation on a bank account to witness the effects of all previous \cf{deposit}
and \cf{withdraw} operations performed on the same bank account in the same
session. We can conceive an alternative contract ($\cv_{gb}^2$) for
\cf{getBalance} to express this consistency requirement:

@@

\noindent To final contract ($\cv_{gb}$) of the \cf{getBalance} operation is
merely a conjunction of the previous two versions ($\cv_{gb}^1$ and
$\cv_{gb}^2$):

>>>>

To prevent \cf{getBalance} from ever showing a negative balance, it is
necessary to prevent the scenario depicted in
fig.~\ref{fig:negativeBalanceAnomaly}. Let $\cureff$ stand for the effect
emitted by the \cf{getBalance} operation. If the effect ($b$) of a withdraw
operation is visible to $\cureff$, and the effect ($a$) of a deposit operation
is visible to the effect ($b$) of the withdraw operation, then it must be the
case that $a$ is also visible to $\cureff$. A contract ($\cv_{gb}^1$) for
\cf{getBalance} operation that precisely captures this application-level consistency
requirement can be written thus:

@@

\noindent To prevent the missing update anomaly described in
fig.~\ref{fig:missingUpdateAnomaly}, it is necessary for a \cf{getBalance}
operation on a bank account to witness the effects of all previous \cf{deposit}
and \cf{withdraw} operations performed on the same bank account in the same
session. We can express an additional contract ($\cv_{gb}^2$) for
\cf{getBalance} that captures this consistency requirement:

@@

The final contract ($\cv_{gb}$) of the \cf{getBalance} operation is
merely a conjunction of the previous two versions ($\cv_{gb}^1$ and
$\cv_{gb}^2$):
